### 2013-10-28 phd/menger.tex
Finished presentation, cleaned up some asrc stuff as well as forcing argument

  \begin{proof}
    Result due to (???)

@@

    The other direction is based upon Gruenhage's topological game presentation. Assume $X$ is Menger, and consider a strategy for $C$ in $\mengame{X}$.

@@

  \begin{theorem}
    A space $X$ is $\sigma$-(relatively compact) if and only if $F \markwin \mengame{X}$.
  \end{theorem}

  \begin{proof}
    For the forward implication, let $X=\bigcup_{n<\omega}R_n$ for $R_n$ relatively compact, and define $\sigma(\mc U,n)$ to be a finite subcover of $R_n$. The previous lemma proves the other direction.
  \end{proof}

@@

  \begin{example}
  Let $R$ be given the topology from example 63 from Counterexamples in Topology, the topology generated by open intervals with countable sets removed. This space is non-regular, non-$\sigma$-compact, and Lindel\"of. It is also Menger as $F \win \mengame{R}$, but $F \not\markwin \mengame{R}$.
  \end{example}

  \begin{proof}
  From Counterexamples: The irrationals are open, but contain no closed neighborhood, showing non-regular. Compact subsets are exactly finite subsets, showing non-$\sigma$-compact.

@@

  There cannot be a winning Markov strategy $\sigma(\mc{U},n)$, however. Define 
      \[
        R_n = \bigcap_{\mc{U}\in\mathfrak{C}} \bigcup\sigma(\mc{U},n)
      \]
  where $\mathfrak{C}$ is the collection of open covers of $R$. For any $x_0,x_1,\dots \in R$, we may define the open cover $\mc{U} = \{R \setminus \{x_i: i \not= n\} : n < \omega \}$, and observe that $\bigcup \sigma(\mc{U},n) \supseteq R_n$ contains only finitely many $x_i$. Thus $R_n$ is finite, but since the previous lemma requires $\bigcup_{n<\omega} R_n = R$ if $\sigma$ is a winning strategy, there exists a counter to $\sigma$.
  \end{proof}

  \begin{example}
  Let $R$ be given the topology from example 67 from Counterexamples in Topology, the topology generated by open intervals with or without the rationals removed. This space is non-regular, non-$\sigma$-compact, and Lindel\"of.

  This space is an example of non-$\sigma$-compact but $F \markwin \mengame{R}$ (and is thus also Menger).
  \end{example}

  \begin{proof}
  From Counterexamples: The rationals are closed, but the closure of any open neighborhood is the whole real line, so they cannot be separated from any irrational point. Compact sets in this topology are nowhere dense in the Euclidean topology, so there cannot be countably many which union to the whole space. $\{(a,b)\setminus D : a,b\in\mathbb{Q},D\in\{\emptyset,\mathbb{Q}\}\}$ is a countable base for the space, and second-countability implies Lindel\"of.

  % To see Menger, let $\mc{U}_0,\mc{U}_1,\dots$ be a sequence of open covers, and choose open sets $U_{2n}\in\mc{U}_{2n}$ which cover $q_n$ for each $q_n\in\mathbb{Q}$ (which in turn are open in the Euclidean line). Since the complement of the union $\bigcup_{n<\omega} U_{2n}$ must be closed discrete in the Euclidean line, it is countable, so open sets $U_{2n+1}\in\mc{U}_{2n+1}$ may be found to cover the remainder.

  To see $F \markwin \mengame{R}$, we define $\sigma(\mc{U}_{2n},2n)$ to be a finite cover of $[-n,n]\setminus\mathbb{Q}$, and $\sigma(\mc{U}_{2n+1},2n+1)$ to be a finite cover of $\{q_n\}$ for each $q_n\in\mathbb{Q}$.
  \end{proof}

@@

    Let $\mathfrak{C}$ collect all the open covers of $X$. We say $X$ is \scish~if there exists a function $f:\mathfrak{C}\times\omega\to\mc{P}(X)$ such that:
      \begin{itemize}
        \item $f(\mc{V},n)$ is $\mc{V}$-compact
        \item $f(\mc{V},n)\cap f(\mc{V},n+1) = \emptyset$
        \item $\bigcup_{n<\omega}f(\mc{V},n)=X$
        \item The set
          \[
            g(\mc{U},\mc{V},n+1) = \bigcup_{p\geq n} \Big(f(\mc{U},p+1)\setminus f(\mc{V},p+1)\Big)\setminus \bigcup_{m\leq n}f(\mc{U},m+1)
          \]
         is $\mc{V}$-compact
      \end{itemize}
  \end{definition}

  Obviously $\sigma$-(relatively compact) implies \scish~implies Lindel\"of. We shall see that the non-$\sigma$-(relatively compact) space $\omega_1^\dagger$ is \scish.

  \begin{definition}
    For two functions $f,g$ we say $f$ is \textbf{$\mu$-almost compatible} with $g$ ($f\al\perp_\mu g$) if $|\{x\in\dom(f)\cap\dom(g):f(x)\not=g(x)\}|<\mu$. If $\mu=\omega$ then we say $f,g$ are \textbf{almost compatible} ($f\al\perp g$).
  \end{definition}

  \begin{lemma}\label{kunlem}
    For each $\alpha<\omega_1$, there exist injective functions $f_\alpha:\alpha\to\omega$ such that if $\alpha<\beta$, then \[f_\alpha \al\perp f_\beta\] that is, $f_\alpha$ and $f_\beta\rest\alpha$ agree on all but finitely many ordinals. In addition, the range of each $f_\alpha$ is co-infinite.
  \end{lemma}

@@

    Finally, suppose $\gamma$ is the limit of $\alpha_0,\alpha_1,\dots$, and $f_\alpha$ is defined for $\alpha<\gamma$. Let $g_0=f_{\alpha_0}$, and assuming $g_n\al\perp f_{\alpha_n}$ with coinfinite range, define $g_{n+1}:\alpha_{n+1}\to\omega$ so that $g_{n+1}\rest\alpha_n=g_n$ and $g_{n+1}\rest(\alpha_{n+1}\setminus\alpha_n)\al\perp f_{\alpha_{n+1}}$ with coinfinite range. Then $g=\bigcup_{n<\omega} g_n$ is an injective function from $\gamma \to \omega$ and $g \al\perp f_\alpha$ for $\alpha <\gamma$, but the range need not be coinfinite. So let
    \[
      f_\gamma(\beta) = \left\{
      \begin{array}{ll}
        g(\alpha_{2n}) & \beta = \alpha_n \\
        g(\beta) & \text{otherwise}
      \end{array}
      \right.
    \]
    which frees up $\{g(\alpha_{2n+1}):n<\omega\}$ from the range of $f_\gamma$, and allows $f_\gamma\al\perp f_\alpha$.
  \end{proof}

@@

  \begin{proof}
    Take the injective funcions $f_\alpha$ from Kunen's lemma such that $f_\alpha \al\perp f_\beta$. For each open cover $\mc V$ of $\oneptlind{\omega_1}$ let $\gamma(\mc V)$ identify the least ordinal such that $[\gamma(\mc V),\omega_1)\cup\{\infty\}$ is in a refinement of $\mc V$. Then $f$ defined by $f(\mc V,0)=[\gamma(\mc V),\omega_1)\cup\{\infty\}$ and $f(\mc{V},n+1) = f_{\gamma(\mc V)}^{-1}(\{n\})$ is easily seen to witness the property.
  \end{proof}

@@

  \begin{proof}
    Let $\sigma(\mc{U}_0,0)$ cover $f(\mc{U}_0,0)$, and let $\sigma(\mc{U}_n,\mc{U}_{n+1},n+1)$ cover $\bigcup_{m\leq n+1}f(\mc{U}_{n+1},m)$ and $g(\mc{U}_n,\mc{U}_{n+1},n+1)$. If $\mc{U}_0,\mc{U}_1,\dots$ is any play by $C$, then for each $x\in X$, we note that one of the following must occur:
      \begin{itemize}
        \item $x \in f(\mc U_0,0)$ and is covered in the initial round.
        \item $x \in f(\mc U_0,P+1)$ for some $P\geq 0$ and:
        \begin{itemize}
          \item $x\in \bigcup_{m\leq n\leq P} f(\mc{U}_{n+1},m+1)$ and is covered by the strategy by round $P+1$.
          \item $x\in \bigcap_{n\leq P} f(\mc{U}_{n+1},P+1)$ and is covered by the strategy during round $P+1$.
          \item For some $n \leq P$, 
            \[x \in \Big( f(\mc{U}_{n},P+1)\setminus f(\mc{U}_{n+1},P+1) \Big)\setminus \bigcup_{m\leq n} f(\mc{U}_{n+1},m+1) \subseteq g(\mc{U}_m,\mc{U}_{m+1},m+1)\]
           and is covered during round $n+1$.
         \end{itemize}
      \end{itemize}
  \end{proof}

@@

  \begin{definition} 
    The statement $S(\kappa,\mu,\lambda)$ due to Scheepers is shorthand for the following: there exist injective functions $f_A:A\to\lambda$ for each $A\in[\kappa]^\mu$ such that $f_A\al\perp_\mu f_B$ for all $A,B\in[\kappa]^\mu$.
  \end{definition}

@@

  \begin{proof}
    Take the injective funcions $f_A:A\to\omega$ witnessing $S(\kappa,\omega,\omega)$. For each cover $\mc V$ of $\oneptlind{\kappa}$ let $A(\mc V)$ define a set such that $\oneptlind{\kappa}\setminus A(\mc V)$ is in a refinement of $\mc V$. Then define $f$ by $f(\mc V,0)=\oneptlind{\kappa}\setminus A(\mc V)$ and $f(\mc{V},n+1) = f_{A(\mc V)}^{-1}(\{n\})$.

    \begin{itemize}
      \item $f(\mc{V},n)$ is $\mc{V}$-compact by definition.
      \item $f(\mc{V},n)\cap f(\mc{V},n+1) = \emptyset$ by definition.
      \item $\bigcup_{n<\omega}f(\mc{V},n)=X$ by definition.
      \item Note that as $f(\mc{U},p+1)=f^{-1}_{A(\mc U)}(\{p\})$, $f(\mc{V},p+1)=f^{-1}_{A(\mc V)}(\{p\})$, and $f_{A(\mc U)}\al\perp f_{A(\mc V)}$, the set
          \[
            \left(\bigcup_{p<\omega} \Big(f(\mc{U},p+1)\setminus f(\mc{V},p+1)\Big) 
            \setminus A(\mc{U})\right)
            \setminus A(\mc{V})
          \] 
        is finite.

        Thus the set
          \[
            g(\mc{U},\mc{V},n+1) = \bigcup_{p\geq n} \Big(f(\mc{U},p+1)\setminus f(\mc{V},p+1)\Big)\setminus \bigcup_{m\leq n}f(\mc{U},m+1)
          \]
        is $\mc{V}$-compact.
    \end{itemize}
  \end{proof}

@@

  \begin{definition}
    Let $\pok\subset Fn^2([\kappa]^\omega,\omega)$ be such that each $p_A$ is injective, and give it the partial order $\leq$ defined by $q\leq p$ if and only if:
          \begin{itemize}
            \item $\dom(q)\supseteq\dom(p)$
            \item For each $A\in\dom(p)$, $q_A\supseteq p_A$
            \item For each $A,B\in\dom(p)$, if $p_A$ and $p_B$ are not defined for some $\alpha\in A\cap B$, but $q_A$ is, then $q_B$ is also defined for $\alpha$ and $q_A(\alpha)=q_B(x)$. That is, 
              \[
                \alpha\in\dom(q_A)\setminus(\dom(p_A)\cup\dom(p_B))
                \Rightarrow
                \alpha\in\dom(q_B) \text{ and } q_A(x)=q_B(x)
              \]
          \end{itemize}
  \end{definition}

@@

  \begin{theorem}
    $S(\kappa,\omega,\omega)$ is consistent with ZFC for any cardinal $\kappa$.
  \end{theorem}

  \begin{proof}
    If $\kappa\leq\omega_1$, then $S(\kappa,\omega,\omega)$ is a theorem of ZFC - use Lemma \ref{kunlem}.

    Assume $\kappa>\omega_1$; we adapt a forcing argument due to Scheepers. Let $M$ be a countable transitive submodel of ZFC. Consider the c.c.c. poset $\pok$ realized in the model $M$. Let $G$ be a $\pok$-generic filter over $M$.

@@

    For each $A\in [\kappa]^\omega$, note $[\kappa]^\omega\cap M$ is cofinal in $[\kappa]^\omega$, so let $A'\supseteq A$ be in $[\kappa]^\omega\cap M$ and let $f_A=\bigcup_{p\in G}p_{A'}\rest A$. Since $G$ is a $\pok$-generic filter over $M$, it is easily verified (considering the dense sets $D_{A,\alpha}$) that $f_A$ is an injective function from $A$ into $\omega$.

    In addition, for $A,B\in [\kappa]^\omega\cap M$, let $p\in G\cap D_A\cap D_B$. For all $q\leq p$ it follows that $\{\alpha\in \dom(q_A)\cap \dom(q_B): q_A(\alpha)\not= q_B(\alpha)\} \subseteq \dom(p_A)\cup\dom(p_B)$. Thus $|\{\alpha\in A\cap B: f_A(\alpha)\not= f_B(\alpha)\}|<\omega$ and $f_A\al\perp f_B$ for $A,B\in [\kappa]^\omega\cap M$, and it's immediate that $f_A\al\perp f_B$ for $A,B\in[\kappa]^\omega$ as well.

    The $f_A$ witness $S(\kappa,\omega,\omega)$ relativized to $M[G]$.
  \end{proof}

  As a result of this forcing for $\kappa>\omega_1$, $CH$ cannot hold in $M[G]$ (Scheepers points out that $\omega_1<\kappa\leq 2^\omega$). It is an open question whether $S(\kappa,\omega,\omega)$ is a theorem of ZFC+CH or ZFC. Nonetheless,

  \begin{corollary}
    $F\kmarkwin{2}\mengame{\oneptlind{\kappa}}$ is consistent with ZFC.
  \end{corollary}

@@

  % I am error
  % \begin{theorem}
  %   $F\kmarkwin{k}\kfillgame{\kappa} \Rightarrow F\kmarkwin{k}\mengame{\oneptlind{\kappa}}$
  % \end{theorem}

  % \begin{proof}
  %   Assume $\sigma$ is a winning $k$-Mark\"ov strategy for $F\kmarkwin{k}\kfillgame{\kappa}$, where 
  %     \[
  %       \sigma(C_0,0)\subseteq
  %       \dots \subseteq
  %       \sigma(\mc C_0,\dots,\mc C_{k-2},k-2) \subseteq
  %       \sigma(C_0,C_1,\dots,C_{k-1},k-1)
  %     \]
  %   for all $n<\omega$.

  %   For each open cover $\mc U$ of $\oneptlind{\kappa}$, let $C(\mc U)$ be a countable set such that $\oneptlind{\kappa}\setminus C(\mc U)$ is in a refinement of $\mc U$. We define $\tau^*$ as follows:

  %     \[
  %       \tau^*(\mc U_0,0) =
  %       \oneptlind{\kappa}\setminus C(\mc U_0)
  %     \]
  %     \[
  %       \tau^*(\mc U_0,\mc U_1,1) =
  %       \dots =
  %       \tau^*(\mc U_0,\dots,\mc U_{k-2},k-2) =
  %       \emptyset
  %     \]
  %     \[
  %       \tau^*(\mc U_0,\dots,\mc U_{k-1},n+k-1) = 
  %       \sigma(C(\mc U_0),\dots,C(\mc U_{k-1}),n+k-1)
  %     \]

  %   If $\tau$ yields legal open sets covering $\tau^*$, then we claim $\tau$ is a winning strategy. Note that for any attack $\mc U_0,\mc U_1,\dots$ that $\tau$ covers $\oneptlind{\kappa}\setminus C(\mc U_0)$ in the initial round, and also covers
  %     \[
  %       \bigcup_{n<\omega}\sigma(C(\mc U_n),\dots,C(\mc U_{n+k-1}),n+k-1) \supseteq
  %       \bigcup_{n<\omega} C(\mc U_n) \supseteq
  %       C(\mc U_0)
  %     \]
  %   by the game's end.
  % \end{proof}

>>>>

  \begin{proof}
    Result due to Hurewicz.

@@

    Now, assume $X$ is Menger, and consider a strategy for $C$ in $\mengame{X}$.

@@

  \begin{corollary}
    A space $X$ is $\sigma$-(relatively compact) if and only if $F \markwin \mengame{X}$.
  \end{corollary}

@@

  \begin{example}
  Let $R$ be given the topology from example 63 from Counterexamples in Topology, the topology generated by open intervals with countable sets removed. This space is a non-regular example where $F \win \mengame{R}$, but $F \not\markwin \mengame{R}$, that is, $R$ is not $\sigma$-(relatively compact).
  \end{example}

  \begin{proof}
  From Counterexamples: The irrationals are open, but contain no closed neighborhood, showing non-regular.

@@

  For any $A=\{x_n:n<\omega\} \in [R]^\omega$, we may choose the open cover $\mc{U} = \{R \setminus \{x_i: i \not= n\} : n < \omega \}$ of $R$ with no finite subcover. Thus all relatively compact sets are finite, and the countable union of finite sets cannot contain $R$, making $R$ not $\sigma$-(relatively compact).
  \end{proof}

  \begin{example}
  Let $R$ be given the topology from example 67 from Counterexamples in Topology, the topology generated by open intervals with or without the rationals removed. This space is non-regular, and non-$\sigma$-compact, but is second-countable and $\sigma$-(relatively compact).
  \end{example}

  \begin{proof}
  From Counterexamples: The rationals are closed, but the closure of any open neighborhood is the whole real line, so they cannot be separated from any irrational point. Compact sets in this topology are nowhere dense in the Euclidean topology, so there cannot be countably many which union to the whole space. $\{(a,b)\setminus D : a,b\in\mathbb{Q},D\in\{\emptyset,\mathbb{Q}\}\}$ is a countable base for the space.

  To see that $R$ is $\sigma$-relatively compact, it suffices to show that $[a,b]\setminus\mathbb{Q}$ is relatively compact. Let $\mc U$ be a cover of $R$, and let $\mc U'$ fill in the missing rationals for any open set in $\mc U$. There is a finite subcover $\mc V'\subseteq \mc U'$ for $[a,b]$ since $\mc U'$ contains open sets from the Euclidean topology. Let $\mc V= \{V\setminus\mathbb{Q}:V\in V'\}$: this is a finite refinment of $\mc U$ covering $[a,b]\setminus\mathbb{Q}$, so $[a,b]\setminus\mathbb{Q}$ is relatively compact.
  \end{proof}

@@

    We say $X$ is \scish~if there exist functions $r_{\mc V}:X\to\omega$ for each open cover $\mc V$ of $X$ such that both of the following sets are $\mc V$-compact for all open covers $\mc U$, $\mc V$ and $n<\omega$:
      \[
        c(\mc V,n)=\{ x\in X : r_{\mc V}(x)\leq n\}
      \]
      \[
        p(\mc U,\mc V)=\{ x\in X : 0<r_{\mc U}(x)<r_{\mc V}(x)\}
      \]
  \end{definition}

  \begin{definition}
    For two functions $f,g$ we say $f$ is \textbf{$\mu$-almost compatible} with $g$ ($f\alcomp_\mu g$) if $|\{x\in\dom(f)\cap\dom(g):f(x)\not=g(x)\}|<\mu$. If $\mu=\omega$ then we say $f,g$ are \textbf{almost compatible} ($f\alcomp g$).
  \end{definition}

  \begin{lemma}\label{kunlem}
    For each $\alpha<\omega_1$, there exist injective functions $f_\alpha:\alpha\to\omega$ such that if $\alpha<\beta$, then \[f_\alpha \alcomp f_\beta\] that is, $f_\alpha$ and $f_\beta\rest\alpha$ agree on all but finitely many ordinals. In addition, the range of each $f_\alpha$ is co-infinite.
  \end{lemma}

@@

    Finally, suppose $\gamma$ is the limit of $\alpha_0,\alpha_1,\dots$, and $f_\alpha$ is defined for $\alpha<\gamma$. Let $g_0=f_{\alpha_0}$, and assuming $g_n\alcomp f_{\alpha_n}$ with coinfinite range, define $g_{n+1}:\alpha_{n+1}\to\omega$ so that $g_{n+1}\rest\alpha_n=g_n$ and $g_{n+1}\rest(\alpha_{n+1}\setminus\alpha_n)\alcomp f_{\alpha_{n+1}}$ with coinfinite range. Then $g=\bigcup_{n<\omega} g_n$ is an injective function from $\gamma \to \omega$ and $g \alcomp f_\alpha$ for $\alpha <\gamma$, but the range need not be coinfinite. So let
    \[
      f_\gamma(\beta) = \left\{
      \begin{array}{ll}
        g(\alpha_{2n}) & \beta = \alpha_n \\
        g(\beta) & \text{otherwise}
      \end{array}
      \right.
    \]
    which frees up $\{g(\alpha_{2n+1}):n<\omega\}$ from the range of $f_\gamma$, and allows $f_\gamma\alcomp f_\alpha$.
  \end{proof}

@@

  \begin{proof}
    Take the injective funcions $f_\alpha$ from Kunen's lemma such that $f_\alpha \alcomp f_\beta$. For each open cover $\mc V$ of $\oneptlind{\omega_1}$ let $\gamma(\mc V)$ identify the least ordinal such that $\oneptlind{\omega_1}\setminus\gamma(\mc U)$ is in a refinement of $\mc V$. Then $r_{\mc V}$ defined by
      \[
        r_{\mc V}(x) = \left\{
      \begin{array}{ll}
        0 & x\in\oneptlind{\omega_1}\setminus\gamma(\mc V) \\
        f_{\gamma(\mc V)}(x)+1 & x\in\gamma(\mc V)
      \end{array}
      \right.
      \] 
    witnesses the property as $c(\mc V,0)$ is contained in a single open set in $\mc V$, $c(\mc V,n+1)$ is a singleton or empty set, and
      \[
        p(\mc U,\mc V) = \{\alpha<\min(\gamma(\mc U),\gamma(\mc V)) : f_{\gamma(\mc U)}(\alpha)<f_{\gamma(\mc V)}(\alpha)\}
      \]
    is finite.
  \end{proof}

@@

  \begin{proof}
    Let $\sigma(\mc{U}_0,0)$ cover $c(\mc{U}_0,0)$, and let $\sigma(\mc{U}_n,\mc{U}_{n+1},n+1)$ cover both $c(\mc{U}_{n+1},n+1)$ and $p(\mc{U}_n,\mc{U}_{n+1})$. If $\mc{U}_0,\mc{U}_1,\dots$ is any play by $C$, then for each $x\in X$, we note that one of the following must occur:
      \begin{itemize}
        \item $r_{\mc U_0}(x)=0$ and thus $x\in c(\mc U_0,0)\subseteq \bigcup \sigma(\mc{U}_0,0)$.
        \item $r_{\mc U_0}(x)=N+1$ for some $N\geq 0$ and:
        \begin{itemize}
          \item For all $n\leq N$, 
            \[
              n+1< r_{\mc U_{n+1}}(x)\leq N+1
            \] 
            and thus $x\in c(\mc U_{N+1},r_{\mc U_{n+1}}(x))=c(\mc U_{N+1},N+1)$.
          \item For some $n \leq N$,
            \[
              r_{\mc U_{n+1}}(x)< n+1 \leq r_{\mc U_n}(x)< N+1
            \]
            and thus $x\in c(\mc U_{n+1},r_{\mc U_{n+1}}(x))\subseteq c(\mc U_{n+1},n+1)$.
          \item For some $n \leq N$, 
            \[
              n+1 \leq r_{\mc U_n}(x)< N+1 < r_{\mc U_{n+1}}(x)
            \]
           and thus $x\in p(\mc U_n,\mc U_{n+1})$
         \end{itemize}
      \end{itemize}
  \end{proof}

@@

  \begin{definition} 
    The statement $S(\kappa,\mu,\lambda)$ due to Scheepers is shorthand for the following: there exist injective functions $f_A:A\to\lambda$ for each $A\in[\kappa]^\mu$ such that $f_A\alcomp_\mu f_B$ for all $A,B\in[\kappa]^\mu$.
  \end{definition}

  \begin{proposition}
    $\neg S(\kappa,\omega,\omega)$ for $\kappa>2^\omega$
  \end{proposition}

  \begin{proof}
    Let $A_\alpha=\{\alpha\cdot\omega+n:n<\omega\}\in[\kappa]^\omega$ and $f_{A_\alpha}:A_\alpha\to\omega$ be injective for $\alpha<\kappa$. Since there are $\kappa>|[\omega]^\omega|$ different $A_\alpha$, there must be $\alpha,\beta$ where $\text{ran}(f_{A_\alpha})=\text{ran}(f_{A_\beta})$. Then there is no way to define $f_{A_\alpha\cup A_\beta}$ so that it is almost compatible with both $f_{A_\alpha}$ and $f_{A_\beta}$.
  \end{proof}

@@

  \begin{proof}
    Take the injective funcions $f_A:A\to\omega$ witnessing $S(\kappa,\omega,\omega)$. For each cover $\mc V$ of $\oneptlind{\kappa}$ let $A(\mc V)$ define a set such that $\oneptlind{\kappa}\setminus A(\mc V)$ is in a refinement of $\mc V$. Then $r_{\mc V}$ defined by 
      \[
        r_{\mc V}(x) = \left\{
      \begin{array}{ll}
        0 & x\in\oneptlind{\kappa}\setminus A(\mc V) \\
        f_{A(\mc V)}(x)+1 & x\in A(\mc V)
      \end{array}
      \right.
      \]

    witnesses the property as $c(\mc V,0)$ is contained in a single open set in $\mc V$, $c(\mc V,n+1)$ is a singleton or empty set, and
      \[
        p(\mc U,\mc V) = \{\alpha\in A(\mc U)\cap A(\mc V) : f_{A(\mc U)}(\alpha)<f_{A(\mc V)}(\alpha)\}
      \]
    is finite.
  \end{proof}

@@

  \begin{definition}
    Let $\pok\subset Fn^2([\kappa]^\omega,\omega)$ be such that each $p_A$ is injective, and give it the partial order $\leq$ defined by $q\leq p$ if and only if:
          \begin{itemize}
            \item $\dom(q)\supseteq\dom(p)$
            \item For each $A\in\dom(p)$, $q_A\supseteq p_A$
            \item For each $A,B\in\dom(p)$, if $p_A$ and $p_B$ are not defined for some $\alpha\in A\cap B$, but $q_A$ is, then $q_B$ is also defined for $\alpha$ and $q_A(\alpha)=q_B(x)$. That is, for $\alpha\in A\cap B$ 
              \[
                \alpha\in\dom(q_A)\setminus(\dom(p_A)\cup\dom(p_B))
                \Rightarrow
                \alpha\in\dom(q_B) \text{ and } q_A(x)=q_B(x)
              \]
          \end{itemize}
  \end{definition}

@@

  \begin{theorem}
    $S(\kappa,\omega,\omega)+(\kappa=2^\omega)$ is consistent with ZFC for any cardinal $\kappa$ with $cf(\kappa)>\omega$.
  \end{theorem}

  \begin{proof}
    We adapt a forcing argument due to Scheepers. Let $M$ be a countable transitive submodel of ZFC. Consider the c.c.c. poset $\pok$ realized in the model $M$. Let $G$ be a $\pok$-generic filter over $M$.

@@

    For each $A\in [\kappa]^\omega$, note $[\kappa]^\omega\cap M$ is cofinal in $[\kappa]^\omega$, so let $A'\supseteq A$ be in $[\kappa]^\omega\cap M$ and let $f_A=\bigcup_{p\in G\cap D_{A'}}p_{A'}\rest A$. Since $G$ is a $\pok$-generic filter over $M$, it is easily verified (considering the dense sets $D_{A,\alpha}$) that $f_A$ is an injective function from $A$ into $\omega$.

    In addition, for $A,B\in [\kappa]^\omega\cap M$, let $p\in G\cap D_A\cap D_B$. For all $q\leq p$ it follows that $\{\alpha\in \dom(q_A)\cap \dom(q_B): q_A(\alpha)\not= q_B(\alpha)\} \subseteq \dom(p_A)\cup\dom(p_B)$. Thus $|\{\alpha\in A\cap B: f_A(\alpha)\not= f_B(\alpha)\}|<\omega$ and $f_A\alcomp f_B$ for $A,B\in [\kappa]^\omega\cap M$, and it's immediate that $f_A\alcomp f_B$ for $A,B\in[\kappa]^\omega$ as well.

    The $f_A$ witness $S(\kappa,\omega,\omega)$. Since $\kappa\geq 2^\omega$ by $\pok$ c.c.c., and $S(\kappa,\omega,\omega)$ is a contradiction for $\kappa>2^\omega$, we know $\kappa=2^\omega$. 
  \end{proof}

  \begin{corollary}
    For each $\kappa$, $F\kmarkwin{2}\mengame{\oneptlind{\kappa}}$ is consistent with ZFC.
  \end{corollary}

@@
